\documentclass[10pt]{article}
\input{res/head}
\input{res/langhead}

\begin{document}
\pagenumbering{gobble}		% turn off page numbering

\titletable{Latin 101}{Dr. Molinarius}{Assignment 14}{}{Iacomus Guilliamus}{Robertus Gallovidius}

\begin{enumerate}
  \item Decline the following noun-adjective combinations:

    \begin{enumerate}
      \item daring poet

        \begin{nounphrase}{po\=eta, po\=etae}{m}{1st}{audax, audacis}{3rd}
          Nominative  & po\=eta aud\={a}x       & po\=etae aud\={a}c\=es \\\hline
          Genitive    & po\=etae aud\={a}cis    & po\=et\=arum aud\={a}cium \\\hline
          Dative      & po\=etae aud\={a}c\=i   & po\=et\=is aud\={a}cibus \\\hline
          Accusative  & po\=etam aud\={a}cem    & po\=et\=as aud\={a}c\=es \\\hline
          Ablative    & po\=et\=a aud\={a}c\=i  & po\=et\=is aud\={a}cibus \\\hline
        \end{nounphrase}

      \item strong man

        \begin{nounphrase}{vir, vir\=i}{m}{2nd}{fortis, fortis}{3rd}
          Nominative  & vir fortis      & vir\=i fort\=es \\\hline
          Genitive    & vir\=i fortis   & vir\=orum fortium \\\hline
          Dative      & vir\=o fort\=i  & vir\=is fortibus \\\hline
          Accusative  & virum fortem    & vir\=os fort\=es \\\hline
          Ablative    & vir\=o fort\=i  & vir\=is fortibus \\\hline
        \end{nounphrase}

      \item sharp wound

        \begin{nounphrase}{vulnus, vulneris}{n}{3rd}{\=acre, \=acris}{3rd}
          Nominative  & vulnus \=acre       & vulnera \=acria \\\hline
          Genitive    & vulneris \=acris    & vulnerum \=acrium \\\hline
          Dative      & vulner\=i \=acr\=i  & vulneribus \=acribus \\\hline
          Accusative  & vulnus \=acre       & vulnera \=acria \\\hline
          Ablative    & vulnere \=acr\=i    & vulneribus \=acribus \\\hline
        \end{nounphrase}
    \end{enumerate}

  \item Translate the following sentences into Latin:

    \begin{tabu}to \linewidth {XX}
      of the easy language & linguae facilis \\
      to/for the fierce legions & legionibus \=acribus \\
      under the beautiful sky & sub cael\=o pulchr\=o \\
      in great grief & in dol\=ore magn\=o \\
      by/with/from strong bodies & corporibus fortibus \\
      of the bold girls & puell\=arum aud\=acium \\
      short months (as subject) & mens\=es br\=ev\=es \\
      by/with/from a strong mind & mente fort\=i \\
      easy wars (direct object) & bella facilia \\
      into the enemy's fierce city & in urbem \=acrem hostis \\
    \end{tabu}

  \item Translate the following sentences into English:

    \begin{tabu}to \linewidth {XX}
      Vulnus m\=ilit\=i dol\=orem facit. & The wound causes pain to the soldier. \\
      Virt\=utem f\=emin\=arum fortium laud\=emus. & Let us praise the courage of the strong women. \\
      \=E dol\=oribus \=acribus disc\=i potest v\=erit\=as. & From sharp pains can the truth be learned. \\
      \=Acr\=es ment\=es habent linguae Lat\=inae discipul\=i et discipulae. & The male and female students of the Latin language have sharp minds. \\
      L\=uce s\=olis fl\=or\=es pulchr\=i gignuntur. & The beautiful flowers are beget by the light of the sun. \\
      \=Acr\=i in bell\=o vir\=i fort\=es bon\=ique caeduntur. & The strong and good men are slain in the fierce war. \\
      In locum miserum congregantur servae domin\=i \=acris. & The female slaves of the fierce lord are gathered in the miserable location. \\
      Fort\=es este, puer\=i et puellae! & Be strong, boys and girls! \\
      Deum aeternum, n\=on v\=itam brevem, col\=amus. & Let us worship everlasting god, not short life. \\
      V\=erit\=atem vid\=ere facile n\=on est. & Truth is not easy to see. \\
    \end{tabu}
\end{enumerate}
\end{document}
